Deep Reinforcement Learning for Conservation Decisions

### 2021-06-04 manuscript/manuscript.Rmd
Updating comment for figure 1

<!-- ML: I have some qualms about this figure; I think it can do a bit more to display what is going on. Like perhaps can put dashed arrows within a trial to show that there is continuity between episodes but not continuity across trials. We could also put a dashed box around the trials to this effect as well. In these dashed boxes, we could put smaller hyperparameter boxes to convey that different trials have distinct hyperparameters. I am also not a fan of the object used for neural networks. -->
\begin{figure}
\includegraphics[width=\linewidth]{fig1.pdf}
\caption{Deep Reinforcement Learning:  An artificial intelligence \emph{agent} uses a \emph{neural network} to select an \emph{action} in response to an \emph{observation} of the \emph{environment}, receiving a \emph{reward} (or punishment) from the environment as a result.  The agent is \emph{trained} to maximize the reward through the experience of trying different actions over repeated \emph{epsiodes} of interacting with the environment.  Over the course of training, the agent adjusts parameter weights on the neural network as it learns which actions lead to the best cumulative rewards. A researcher may \emph{tune} an agent by considering iterative trials that train different agents with different \emph{hyperparameters}, such as different neural network architectures.  An agent trained with the most successful combination of hyperparameters can then be tested in an evaluation environment.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{fig1.pdf}
\caption{Deep Reinforcement Learning:  A deep RL \emph{agent} uses a \emph{neural network} to select an \emph{action} in response to an \emph{observation} of the \emph{environment}, and receives a \emph{reward} from the environment as a result. During \emph{training}, the agent tries to maximize its cumulative reward by interacting with the environment and learning from experience. In the RL loop, the agent performs an action, and the environment returns a reward as well as an observation of the environment's state. The agent-environment loop continues until the environment reaches a terminal state, after which the environment will reset, causing a new \emph{episode} to begin. Across training episodes, the agent will continually update the \emph{parameters} in its neural network, so that the agent will select better actions. Before training starts, the researcher must input a set of \emph{hyperparameters} to the agent; hyperparameters direct the learning process and thus affect the outcome of training. A researcher finds the best set of hyperparameters during \emph{tuning}. Hyperparameter tuning consists of iterative \emph{trials}, in which the agent is trained with different sets of hyperparameters. At the end of a trial, the agent is evaluated to see which agent attains the highest cumulative reward. An agent is \emph{evaluated} by recording the cumulative reward over one episode, or the mean reward over multiple episodes. Within evaluation, the agent does not update its neural network; instead, the agent only uses the neural network to select actions.}
\end{figure}
